%% Abstract (configurado para língua inglesa)
\begin{resumo}[Abstract]			% Título do Resumo (Abstract = Resumo em inglês)
\begin{otherlanguage*}{english}		% Língua do texto
  The purpose of social networks is to share knowledge and information. With the great popularization of the Internet, social networks have become virtualized, meeting the needs of communication and real-life relationships using the virtual environment. In parallel to the evolution of the internet and social networks, another area that has grown enormously was vegetarianism and veganism. Many of the adherents of this diet begin this practice due to issues related to health, economy, environment, ethics and religion. In pursuit of adequate food, many followers choose to start making their own meals rather than going to restaurants. The present work presents the development of a mobile application implemented in the Ionic hybrid platform, which produces executable code for the IOS 7+ and Android 4.2+ operating environments, as well as integrated with Facebook. The application will act as a social network, where users can post recipes, make them available to everyone who is using the app. They can enjoy, favor and comment on the published recipe as well as follow who posted the recipe, thus creating a social bond within the application.
  
\vspace{\onelineskip}
\noindent\\
\textbf{Keywords}: Social networks, vegetarianism, veganism, mobile application, Ionic, IOS, Android, Facebook.
\end{otherlanguage*}
\end{resumo}

%% Exemplo de resumo em francês
%\begin{resumo}[Résumé]
% \begin{otherlanguage*}{french}
%    Il s'agit d'un résumé en français.
% 
%   \textbf{Mots-clés}: latex. abntex. publication de textes.
% \end{otherlanguage*}
%\end{resumo}

%% Exemplo de resumo em Espanhol
%\begin{resumo}[Resumen]
% \begin{otherlanguage*}{spanish}
%   Este es el resumen en español.
%  
%   \textbf{Palabras clave}: latex. abntex. publicación de textos.
% \end{otherlanguage*}
%\end{resumo}
% ---